---
title: "An implementation of the Panning Algorithm"
author: "Samuel Orso"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An implementation of the Panning Algorithm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document illustrates how to use the panning package as a feature selection 
method. 

# Data Simulation

Within this section, we generate a set of data to be used within the panning
analysis. 

```{r eval = FALSE}
# Simulate data
n <- 50

# Number of betas (includes intercept)
p <- 40

# Set seed for reproducibility of data generation
set.seed(123)

# Create a vector of betas
beta <- c(1, rpois(p - 1, lambda = 0.5))

# Create design matrix
X <- matrix(rnorm((p-1)*n), nrow=n, ncol=(p-1))

# Generate a vector for predictions
y <- rbinom(n,1,1/(1+exp(-tcrossprod(beta, cbind(1, X)))))
```


# Panning Algorithm Configuration

There are many options afforded to users of panning from specifying the 
number of folds done in the cross validation to the amount of processing power
to use. Generally, the top options users will frequently need to modify are 
the following:

```{r eval = FALSE}
alpha <- 1e-3 # Level of the quantile of the prediction errors.
B     <- 1e3  # Number of Bootstraps to Perform
dmax  <- 8L   # Number of Model Features to Consider
proc  <- 2L   # Number of CPUs to use (typically 2-4 on PC and 12-16 on clusters)
```

# Panning Algorithm Implementation

Due to the fine grain nature of panning, we have opted to allow the user to have
maximum flexibility while customizing the routine of panning. As a result of the 
design decision, this has led to have a user to create a defined loop that takes
initial results from `InitialStep()` and iterates over the `GeneralStep()`
until the maximum feature is desired. In the future, we may develop a
all-in-one function called `panning()` that alleviates this need.

```{r eval = FALSE}
# Create a storage vector to retain each "step"
panning_results <- vector("list",dmax)

# Run the initial step algorithm
IStep <- InitialStep(y = y, X = X, family = binomial(link = "logit"),
                     type = "response", divergence = "classification",
                     trace = FALSE)

# Save results
covariates <- IStep$Ids

# Store the IStep values into Panning Results
panning_results[[1]] <- IStep

# Step through the model
for(d in 2:dmax){
  
  message("Working on models with ", d, " features...")
  
  # Compute the General Step
  GStep <- GeneralStep(y = y, X = X, Id_1s = covariates, d = d, B = B,
                       family = binomial(link = "logit"), type = "response",
                       divergence = "classification", trace = FALSE, proc = proc)
  
  
  # Update values
  covariates <- GStep$Ids
  
  # Save results
  panning_results[[d]] <- GStep
}

# Store results
save(panning_results, file = "panning_data.rda")
```
